dads manual

### 2020-12-09 inst/gitbook/03_make.modifiers.Rmd
typos

## Setting some parameters for generating trees
bd_params  <- list(extinction = 0)
stope_rule <- list(max.living = 20)

## Generating a tree with the default branch length parameter
set.seed(0)
default_tree <- dads(bd.params = bd_params,
                     stop.rule = stope_rule,
                     modifiers = default_modifiers)
```

@@

## Generating a new tree with this modifier
set.seed(0)
modified_tree <- dads(bd.params = bd_params,
                      stop.rule = stope_rule,
                      modifiers = constant_modifier)
```

@@

## Generating a new tree with this modifier
set.seed(0)
increasing_tree <- dads(bd.params = bd_params,
                        stop.rule = stope_rule,
                        modifiers = increasing_modifier)
```

@@

```{r}
## A modifier for selection
ladderised_modifier <- make.modifiers(selection = select.last)
## Generating a new tree with this modifier
set.seed(0)
ladderised_tree <- dads(bd.params = bd_params,
                        stop.rule = stope_rule,
                        modifiers = ladderised_modifier)
## Displaying the results
par(mfrow = c(1,2))
plot(default_tree,    main = "Default modifier")
plot(ladderised_tree, main = "Ladderising modifier")
```

@@

## Simulate a tree and trait with no modifier
set.seed(1)
default_dads <- dads(bd.params = bd_params,
                     stop.rule = stope_rule,
                     traits    = BM_trait)

## Simulate a tree and trait with the modifier
set.seed(1)
skewed_trait_dads <- dads(bd.params = bd_params,
                          stop.rule = stope_rule,
                          traits    = BM_trait,
                          modifiers = positive_skew)

@@

## Generating a new tree with this modifier
set.seed(0)
modified_tree <- dads(bd.params = bd_params,
                      stop.rule = stope_rule,
                      modifiers = random_extinction)

@@

## Simulate a tree and trait with the modifier
set.seed(1)
biased_trait_dads <- dads(bd.params = bd_params,
                          stop.rule = stope_rule,
                          traits    = BM_trait,
                          modifiers = biased_trait)

>>>>

## Setting some parameters for generating trees
bd_params <- list(extinction = 0)
stop_rule <- list(max.living = 20)

## Generating a tree with the default branch length parameter
set.seed(0)
default_tree <- dads(bd.params = bd_params,
                     stop.rule = stop_rule,
                     modifiers = default_modifiers)
```

@@

## Generating a new tree with this modifier
set.seed(0)
modified_tree <- dads(bd.params = bd_params,
                      stop.rule = stop_rule,
                      modifiers = constant_modifier)
```

@@

## Generating a new tree with this modifier
set.seed(0)
increasing_tree <- dads(bd.params = bd_params,
                        stop.rule = stop_rule,
                        modifiers = increasing_modifier)
```

@@

```{r}
## A modifier for selection
ladderised_modifier <- make.modifiers(selection = select.last)
## Generating a new tree with this modifier
set.seed(0)
ladderised_tree <- dads(bd.params = bd_params,
                        stop.rule = stop_rule,
                        modifiers = ladderised_modifier)
## Displaying the results
par(mfrow = c(1,2))
plot(default_tree,    main = "Default modifier")
plot(ladderised_tree, main = "Ladderising modifier")
```

@@

## Simulate a tree and trait with no modifier
set.seed(1)
default_dads <- dads(bd.params = bd_params,
                     stop.rule = stop_rule,
                     traits    = BM_trait)

## Simulate a tree and trait with the modifier
set.seed(1)
skewed_trait_dads <- dads(bd.params = bd_params,
                          stop.rule = stop_rule,
                          traits    = BM_trait,
                          modifiers = positive_skew)

@@

## Generating a new tree with this modifier
set.seed(0)
modified_tree <- dads(bd.params = bd_params,
                      stop.rule = stop_rule,
                      modifiers = random_extinction)

@@

## Simulate a tree and trait with the modifier
set.seed(1)
biased_trait_dads <- dads(bd.params = bd_params,
                          stop.rule = stop_rule,
                          traits    = BM_trait,
                          modifiers = biased_trait)

### 2020-12-09 inst/gitbook/index.Rmd
typos + minors
typos

# `dads`

Disparity and diversity simulations.

@@

## Installing the latest version directly from GitHub
install_github("TGuillerme/dads")
```

```{r, eval = FALSE, echo = FALSE, message = FALSE}
## loading the package and setting up the start seed.
library(dads)
## Setting a random seed for repeatability
set.seed(123)
```

>>>>

# `dads`: disparity and diversity simulations.

@@

## Installing the latest version directly from GitHub
devtools::install_github("TGuillerme/dads")
```

```{r, eval = FALSE, echo = FALSE, message = FALSE}
## Loading the package and setting up the start seed.
library(dads)
```
